---
title: "Final Project"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
```


```{r}
getwd()
Repcandidates <- read_csv("/Users/srijitadatta/Documents/FinalProject/data/schedule_a-2022-04-09T18_08_05.csv")
Demcandidates <- read_csv("/Users/srijitadatta/Documents/FinalProject/data/schedule_a-2022-04-10T12_46_53DEM.csv")
```

Q1) Which Republican and Democrat candidate got the most contribution from MO?

#REPUBLICAN

```{r}
Repcandidates %>%
  filter(contributor_state == "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```

```{r}

Repcandidates %>%
  filter(contributor_state != "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```


#DEMOCRATIC

```{r}
Demcandidates %>%
  filter(contributor_state == "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```

```{r}
Demcandidates %>%
  filter(contributor_state != "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```


Q2) Which candidate has got the greatest number of contributions?

#REPUBLICAN

```{r}
Repcandidates %>%
  count(committee_name...2) %>%
  arrange(desc(n))

```

#DEMOCRATIC

```{r}

Demcandidates %>%
  count(committee_name...2) %>%
  arrange(desc(n))

```

Q3) Which republican and democratic candidate got the most contributions from Retired persons ?

```{r}
Repcandidates %>%
  filter(contributor_employer == "RETIRED" & contributor_state == "MO" ) %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))
```
#Democratic

```{r}

Demcandidates %>%
  filter(contributor_employer == "RETIRED" & contributor_state == "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```

Q4)Which ZIP Code contributed the most amount within MO? 

#Republican

```{r}
Repcandidates %>%
  filter(contributor_state == "MO") %>%
  group_by(contributor_zip) %>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))
```
63080

#Democratic

```{r}
Demcandidates %>%
  filter(contributor_state == "MO") %>%
  group_by(contributor_zip) %>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```
63028

Q5) Which candidate received the most money from the ZIP code that contributed the most 
money? How much?

#Republican

```{r}
Repcandidates %>%
  filter(contributor_state == "MO" & contributor_zip == "63080") %>%
  group_by(committee_name...2) %>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```

#Democratic

```{r}
Demcandidates %>%
  filter(contributor_state == "MO" & contributor_zip == "63028") %>%
  group_by(committee_name...2) %>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```

#---------------------------------------------------------------------------



```{r}
Cand_finance <- read_csv("/Users/srijitadatta/Documents/FinalProject/data/campaignfinancedata.csv")

```

