---
title: "Final Project"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
```


```{r}
getwd()
Repcandidates <- read_csv("/Users/srijitadatta/Documents/FinalProject/data/schedule_a-2022-04-09T18_08_05.csv")
Demcandidates <- read_csv("/Users/srijitadatta/Documents/FinalProject/data/schedule_a-2022-04-10T12_46_53DEM.csv")
```

Q1) Which Republican and Democrat candidate got the most contribution from MO?

#REPUBLICAN

```{r}
Repcandidates %>%
  filter(contributor_state == "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```

```{r}

Repcandidates %>%
  filter(contributor_state != "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```


#DEMOCRATIC

```{r}
Demcandidates %>%
  filter(contributor_state == "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```

```{r}
Demcandidates %>%
  filter(contributor_state != "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```


Q2) Which candidate has got the greatest number of contributions?

#REPUBLICAN

```{r}
Repcandidates %>%
  count(committee_name...2) %>%
  arrange(desc(n))

```

#DEMOCRATIC

```{r}

Demcandidates %>%
  count(committee_name...2) %>%
  arrange(desc(n))

```

Q3) Which republican and democratic candidate got the most contributions from Retired persons ?

```{r}
Repcandidates %>%
  filter(contributor_employer == "RETIRED" & contributor_state == "MO" ) %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))
```
#Democratic

```{r}

Demcandidates %>%
  filter(contributor_employer == "RETIRED" & contributor_state == "MO") %>%
  group_by(committee_name...2) %>%
  summarise(total_cont=sum(contribution_receipt_amount)) %>%
  arrange(desc(total_cont))

```

Q4)Which ZIP Code contributed the most amount within MO? 

#Republican

```{r}
Repcandidates %>%
  filter(contributor_state == "MO") %>%
  group_by(contributor_zip) %>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))
```
63080

#Democratic

```{r}
Demcandidates %>%
  filter(contributor_state == "MO") %>%
  group_by(contributor_zip) %>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```
63028

Q5) Which candidate received the most money from the ZIP code that contributed the most 
money? How much?

#Republican

```{r}
Repcandidates %>%
  filter(contributor_state == "MO" & contributor_zip == "63080") %>%
  group_by(committee_name...2) %>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```

#Democratic

```{r}
Demcandidates %>%
  filter(contributor_state == "MO" & contributor_zip == "63028") %>%
  group_by(committee_name...2) %>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```

#---------------------------------------------------------------------------



```{r}
Cand_finance <- read_csv("/Users/srijitadatta/Documents/FinalProject/data/campaignfinancedata.csv")

```

How much money has been raised in total (nationwide) for election campaign?

```{r}
Cand_finance %>% 
summarise(total=sum(TTL_RECEIPTS))
```
2.683 B

How much money was raised by Democrat and Republican candidates? (nationwide)
#REP
```{r}
Cand_finance %>% 
  filter(CAND_PTY_AFFILIATION=="REP") %>% 
  summarise(total=sum(TTL_RECEIPTS))
```
1.0424 B
#DEM
```{r}
Cand_finance %>% 
  filter(CAND_PTY_AFFILIATION=="DEM") %>% 
  summarise(total=sum(TTL_RECEIPTS))
```

How much money has been raised by candidates running from Missouri?
```{r}
Cand_finance %>% 
  filter(CAND_OFFICE_ST=="MO") %>% 
  summarise(total=sum(TTL_RECEIPTS))
```
44.2 Million

Howm much has been raised by Republican and Democrat candidates in Missouri?
#REP
```{r}
Cand_finance %>% 
  filter(CAND_OFFICE_ST=="MO" & CAND_PTY_AFFILIATION=="REP") %>% 
  summarise(total=sum(TTL_RECEIPTS))
```
35.74 Million

#DEM
```{r}
Cand_finance %>% 
  filter(CAND_OFFICE_ST=="MO" & CAND_PTY_AFFILIATION=="DEM") %>% 
  summarise(total=sum(TTL_RECEIPTS))
```
8.455 Million
How much money has been raised by candidates in other states?
```{r}
Cand_finance %>% 
group_by(CAND_OFFICE_ST) %>% 
summarise(total=sum(TTL_RECEIPTS)) %>% 
arrange(desc(total))
```
Total number of Democrats vs. Republicans running for election? (nationwide and state)
#Nationwide
```{r}
Cand_finance %>% 
  count(CAND_PTY_AFFILIATION) %>%
arrange (desc(n))
```
#state
```{r}
Cand_finance %>% 
  filter(CAND_OFFICE_ST=="MO") %>% 
  count(CAND_PTY_AFFILIATION) %>% 
  arrange(desc(n))

```

How much did party committees contribute to candidates in MO with respect to entire US?
#entire US
```{r}
Cand_finance %>%
summarise(total=sum(POL_PTY_CONTRIB))
```
1.161 Million
#state
```{r}
Cand_finance %>%
filter(CAND_OFFICE_ST=="MO") %>%
summarise(total=sum(POL_PTY_CONTRIB))
```
How many candidates are there who do not have a state affiliation?
```{r}
Cand_finance %>% 
  count(CAND_OFFICE_ST=="0")
```
What is the total debt owed by Republican and Democrat candidates in Missouri vs. entire U.S.?
#Reps in MO
```{r}
Cand_finance %>%
filter(CAND_OFFICE_ST =="MO" & CAND_PTY_AFFILIATION == "REP") %>%
summarise( total = sum(DEBTS_OWED_BY))
```
#Reps in US
```{r}
Cand_finance %>%
filter(CAND_PTY_AFFILIATION=="REP") %>%
summarise(total=sum(DEBTS_OWED_BY))
```
#Dems in MO
```{r}
Cand_finance %>%
filter(CAND_OFFICE_ST =="MO" & CAND_PTY_AFFILIATION == "DEM") %>%
summarise(total = sum(DEBTS_OWED_BY))
```
0.358 Million
#Dems in US
```{r}
Cand_finance %>%
filter( CAND_PTY_AFFILIATION == "DEM") %>%
summarise( total = sum( DEBTS_OWED_BY))
```
74.18 Million
Which candidates raised the most money vs. who raised the least? (Both nationwide and state)
#Dems in MO
```{r}
Cand_finance %>%
filter(CAND_OFFICE_ST=="MO" & CAND_PTY_AFFILIATION=="DEM") %>%
summarise(total=sum(TTL_RECEIPTS)) %>%
arrange(desc(total))
```
8.455 Million
#Dems in US
```{r}
Cand_finance %>%
filter(CAND_PTY_AFFILIATION=="DEM") %>%
summarise(total=sum(TTL_RECEIPTS)) %>%
arrange(desc(total))
```
1.612 Billion

#Reps in MO
```{r}
Cand_finance %>%
filter(CAND_OFFICE_ST =="MO" & CAND_PTY_AFFILIATION == "REP") %>%
summarise(total=sum(TTL_RECEIPTS) ) %>%
arrange(desc(total))
```
35.74 Million

#Reps in US
```{r}
Cand_finance %>%
filter(CAND_PTY_AFFILIATION=="REP") %>%
summarise( total=sum(TTL_RECEIPTS)) %>%
arrange(desc(total))
```
1.042 billion

```{r}
Cand_finance %>%
filter(CAND_PTY_AFFILIATION=="DEM" | CAND_PTY_AFFILIATION=="REP") %>%
select(CAND_NAME,TTL_RECEIPTS,CAND_PTY_AFFILIATION ) %>%
arrange(desc(TTL_RECEIPTS))
```
```{r}
Cand_finance %>%
filter(CAND_OFFICE_ST=="MO" & (CAND_PTY_AFFILIATION=="DEM" | CAND_PTY_AFFILIATION == "REP")) %>%
select(CAND_NAME,TTL_RECEIPTS,CAND_PTY_AFFILIATION ) %>%
arrange(desc(TTL_RECEIPTS))
```

How much did Josh Hawley get from MO? From outside MO? Which state contributed the most to Hawley apart from MO?
```{r}
Cand_finance %>%
filter(CAND_OFFICE_ST == "MO" & CAND_NAME ==" Josh Hawley") %>%
summarise( total = sum( TTL_RECEIPTS))
```
```{r}
Cand_finance %>%
filter(CAND_OFFICE_ST!="MO" & CAND_NAME =="Josh Hawley") %>%
group_by(CAND_OFFICE_ST) %>%
summarise(total=sum(TTL_RECEIPTS) %>%
arrange(desc(total))
```

```{r}
source_finance <- read_csv("/Users/srijitadatta/Documents/FinalProject/data/Sourcefinancedata.csv")
```


```{r}

Cand_finance %>%
  filter(grepl('HARTZLER',CAND_NAME))%>%
  select(CAND_NAME, TTL_RECEIPTS)
```

```{r}
source_finance %>%
  filter(committee_name...2 == "VICKY HARTZLER FOR SENATE") %>%
  summarise(total=sum(contribution_receipt_amount))

```
#Source_finance data is not updated since December, hence discrepancies

#MAIN----------------------------------------------------------------------
#Q) Total Individual contributions from MO and US
#from MO
```{r}
Cand_finance %>%
  filter(CAND_OFFICE_ST == "MO") %>%
  summarise(total=sum(TTL_INDIV_CONTRIB))
```
#From US
```{r}
Cand_finance %>%
  filter(CAND_OFFICE_ST !="MO")%>%
  summarise(total=sum(TTL_INDIV_CONTRIB))
```
# Q) Total fund raised by democratic and republican

#Funds Raised by democratic candidates in MO
```{r}
Cand_finance %>%
  filter(CAND_OFFICE_ST == "MO" & CAND_PTY_AFFILIATION == "DEM") %>%
  summarise(total=sum(TTL_RECEIPTS))
```

#Funds Raised by democrats in US

```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "DEM") %>%
  summarise(total=sum(TTL_RECEIPTS))

```

#Funds Raised by republicans in MO
```{r}
Cand_finance %>%
  filter(CAND_OFFICE_ST == "MO" & CAND_PTY_AFFILIATION == "REP") %>%
  summarise(total=sum(TTL_RECEIPTS))
  

```

#Contribution Raised by Republican in US
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "REP") %>%
  summarise(total=sum(TTL_RECEIPTS))
  

```
# Q)Maximum funds by democrats and republican

#Maximum funds by dem candidates in MO and their names
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "DEM" & CAND_OFFICE_ST =="MO") %>%
  summarise(maxi=max(TTL_RECEIPTS),name=CAND_NAME)
```

#Maximum fund by dem candidates outside MO and their names
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "DEM" & CAND_OFFICE_ST !="MO") %>%
  summarise(maxi=max(TTL_RECEIPTS),name=CAND_NAME)
```
#Maximum funds by rep candidates in MO and their names
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "REP" & CAND_OFFICE_ST =="MO") %>%
  summarise(maxi=max(TTL_RECEIPTS),name=CAND_NAME)
```
#Maximum fund by rep candidates outside MO and their names
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "REP" & CAND_OFFICE_ST !="MO") %>%
  summarise(maxi=max(TTL_RECEIPTS),name=CAND_NAME)
```
#Q) Minimum funds by dem and rep candidates in MO and is US

#Minimum fund by dem candidates in MO and their names
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "DEM" & CAND_OFFICE_ST =="MO") %>%
  summarise(mini=min(TTL_RECEIPTS),name=CAND_NAME)
```

#Minimum fund by dem candidates outside MO and their names
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "DEM" & CAND_OFFICE_ST !="MO" ) %>%
  summarise(mini=min(TTL_RECEIPTS),name=CAND_NAME)
```
#Minimum fund by rep candidates in MO and their names
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "REP" & CAND_OFFICE_ST =="MO") %>%
  summarise(mini=min(TTL_RECEIPTS),name=CAND_NAME)
```
#Minimum fund by rep candidates Outside MO and their names
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION == "REP" & CAND_OFFICE_ST !="MO") %>%
  summarise(mini=min(TTL_RECEIPTS),name=CAND_NAME)
```


#Q) All candidates funds, expenditure and in-hand cash
#REP in MO

```{r}
Cand_finance %>%
  filter(CAND_OFFICE_ST =="MO" & CAND_PTY_AFFILIATION =="REP") %>%
  group_by(CAND_NAME) %>%
  select(TTL_RECEIPTS, TTL_DISB,CAND_OFFICE_ST,CAND_PTY_AFFILIATION)
```
#REP in entire US
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION =="REP") %>%
  group_by(CAND_NAME) %>%
  select(TTL_RECEIPTS, TTL_DISB,CAND_OFFICE_ST,CAND_PTY_AFFILIATION)
  
```

#DEM in entire MO
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION =="DEM" & CAND_OFFICE_ST =="MO") %>%
  group_by(CAND_NAME) %>%
  select(TTL_RECEIPTS, TTL_DISB,CAND_OFFICE_ST,CAND_PTY_AFFILIATION)
  
```



#DEM in entire US
```{r}
Cand_finance %>%
  filter(CAND_PTY_AFFILIATION =="DEM") %>%
  group_by(CAND_NAME) %>%
  select(TTL_RECEIPTS, TTL_DISB,CAND_OFFICE_ST,CAND_PTY_AFFILIATION)
```

```{r}
cand_finance_updt_REP <- Cand_finance %>%
  filter(CAND_ID %in% c('S2MO00544','H0MO07113','S2MO00536','H0MO04086','S2MO00627','S2MO00585','S2MO00643','S8MO00160','S0MO00183'))

```

```{r}
cand_finance_updt_DEM <- Cand_finance %>%
  filter(CAND_ID %in% c('S2MO00650','S2MO00551','S2MO00528','S2MO00494','S2MO00692'))

```


```{r}
cand_finance_updt_REP %>%
  summarise(cand_name= CAND_NAME,funds=TTL_RECEIPTS,disbursement=TTL_DISB,state=CAND_OFFICE_ST,inhand_cash=(TTL_RECEIPTS-TTL_DISB), affiliation=CAND_PTY_AFFILIATION)
  
```

```{r}
cand_finance_updt_DEM %>%
  summarise(cand_name= CAND_NAME,funds=TTL_RECEIPTS,disbursement=TTL_DISB,state=CAND_OFFICE_ST,inhand_cash=(TTL_RECEIPTS-TTL_DISB), affiliation=CAND_PTY_AFFILIATION)
  
```


```{r}
source_finance_updt_REP <- read_csv("/Users/srijitadatta/Documents/FinalProject/data/REP_SourceData.csv")
```

```{r}
source_finance_updt_DEM<- read_csv("/Users/srijitadatta/Documents/FinalProject/data/DEM_SourceData.csv")
```

#Data on funding source details were last updated in dec

#Republic Candidates

#fundings from MO
```{r}
source_finance_updt_REP %>%
  filter(contributor_state == "MO") %>%
  group_by(committee_name...2)%>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```
#fundings from outside MO
```{r}
source_finance_updt_REP %>%
  filter(contributor_state != "MO") %>%
  group_by(committee_name...2)%>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```

#Democratic Candidates

#fundings from MO
```{r}
source_finance_updt_DEM %>%
  filter(contributor_state == "MO") %>%
  group_by(committee_name...2)%>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```
#fundings from outside MO
```{r}
source_finance_updt_DEM %>%
  filter(contributor_state != "MO") %>%
  group_by(committee_name...2)%>%
  summarise(total=sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

```

```{r}
election_data<- read_csv("/Users/srijitadatta/Documents/FinalProject/data/electionDATA.csv")
```

#Total number of Democratic and Republic Candidates

```{r}
election_data %>%
  count(party_full) %>%
  arrange(desc(n))

```

```{r}
election_data %>%
  count(incumbent_challenge_full) %>%
  arrange(desc(n))
```

#Democratic

```{r}
election_data%>%
  filter(party_full == "DEMOCRATIC PARTY") %>%
  summarise(name= candidate_name, funds= total_receipts , disb = total_disbursements, inHandCash=total_receipts-total_disbursements)

```

#Republican

```{r}
election_data%>%
  filter(party_full == "REPUBLICAN PARTY") %>%
  summarise(name= candidate_name, funds= total_receipts , disb = total_disbursements, inHandCash=total_receipts-total_disbursements)

```